An Instance Based Reasoning for Empirical Transfer Learning

### 2015-04-09 manuscript.tex
stufff....

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE which works as follows:
\begin{enumerate}
\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

Note that the above requires a distance measure between sets of decisions: GALE uses the standard case-based reasoning measure defined by Aha et al.~\cite{aha91}. Note also that GALE implements step1 via  the FASTMAP~\cite{Faloutsos1995} linear-time
heuristic:
\begin{itemize}
\item Pick any point at random; 
\item Let {\em east} be the point furthest from that point; 
\item Let {\em west} be the point furthest from {\em east}.
\end{itemize}

These final sub-divisions found by this process are the {\em neighborhoods} that GALE will {\em perturb} as follows:
\begin{itemize}
\item Find the objective scores of the {\em east,west} poles in each neighborhood.
\item Using the continuous domination predicate of MOEA, find  the {\em better} pole. 
\item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).
\item Let generation $i+1$ be the combination of all pushed points from all neighborhoods.
\end{itemize}

>>>>

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
WHAT begins by \textit{clustering} the training data into similar subsets using WHERE, which works as follows:
\begin{enumerate}
\item Find two distant points in that population; call them the {\em east} and {\em west} poles. 
\item Draw an axis of length $c$ between the poles. 
\item Let each point be at distance $a,b$ to the {\em east,west} poles.  Using the cosine rule, project each point onto the  axis  at $x=(a^2 + c^2 - b^2)/(2c)$.  
\item Using the median $x$ value, divide the population.
\item For each half that is larger than $\sqrt{N}$ of the original population, go to step 1.
\end{enumerate}

There are couple of things to note: firstly, the above algorithm requires a distance measure between sets of decisions, for this WHERE uses case-based reasoning measure defined by Aha et al.~\cite{aha91}; secondly, in step-1 a linear time heuristic called FASTMAP~\cite{Faloutsos1995} is used to find the two most distant points, this procedure is listed below:
\begin{itemize}
\item Pick a point at random; 
\item Let {\em east} be the point furthest from that point; 
\item Then {\em west} be the point furthest from {\em east}.
\end{itemize}

The final clusters that are found by WHERE are then used by WHAT as follows:
\begin{itemize}
\item Find the objective scores of the {\em east,west} poles in each neighborhood.
\item Using the continuous domination predicate of MOEA, find  the {\em better} pole. 
\item Perturb all points in that neighborhood by pushing them towards the better pole, by a distance  $c/2$ (recall that  $c$ is the distance between the poles).
\item Let generation $i+1$ be the combination of all pushed points from all neighborhoods.
\end{itemize}
